\documentclass{report}
\usepackage{ctex}
\usepackage{enumerate}

\begin{document}
	\chapter{Introduction}
	Eye tracking technique has been widely used in hunman-computer interaction field and usability research.
	
		\section{Motivation}
			\begin{enumerate}
				\item Why studying eye tracking technique in this project? \\
				As computer development i sgrowing rapidly today, with the computer.
				
				\item Why studying scanpath and STA algorithm in this project? \\
				Scanpath is one of the popular eye tracking metrics which hhas been applied.
				
				\item Why studying visual methodology and visualisation techniques in this project? \\
				Visualisation always is a helpful way to explore useful information for researchers.
			\end{enumerate}
		
		\section{Research Questions}
		With the current eye tracking research background mentioned before, and the main purpose of this project.
			\begin{itemize}
				\item What are the differences between STA algorithm and other already existing clustering algorithms?
				
				\item What are the advantages and disadvantages of current visualisation techniques?
			\end{itemize}
		
		\section{Aims}
		One  purpose of this project is to build a web user interface which can call the STA algorithm to generate a trending scanpath and visualise it.
		
		\section{Objectives}
			\begin{enumerate}
				\item In order to better understand the research about eye tracking, scan-path
				
				\item In order to
				
				\item To implement the web
			\end{enumerate}
			
		\section{Deliverables}
			\begin{enumerate}
				\item Creating web user interfaces that the user
				
				\item After loading
			\end{enumerate}
			
		\section{Dissertation Structure}
		The following content of this dissertation is simply introduced in this part
			\begin{itemize}
				\item \textbf{Chapter 2} is the background
				
				\item \textbf{Chapter 3} is the used research methods
				
				\item \textbf{Chapter 4} is the detailed implementation steps of this project.
			\end{itemize}
\end{document}